### 2018-03-15 submission/manuscript.Rmd
update to include normal not control fig 1

**Table 1: Total Individuals in each Study Included in the Fecal Analysis**

@@

**Table 2: Studies with Tissue Samples Included in the Analysis**

@@

**Figure 1: Significant Bacterial Community Metrics for Adenoma or Carcinoma in Feces** A) Adenoma evenness. B) Carcinoma evenness. C) Carcinoma Shannon diversity. Blue represents controls and red represents either adenoma (panel A) or carcinoma (panel B and C). The black lines represent the median value for each repsective group.

**Figure 2: Odds Ratio for Adenoma or Carcinoma based on Bacterial Community Metrics in Feces.** A) Community-based odds ratio for adenoma. B) Community-based odds ratio for carcinoma. Colors represent the different variable regions used within the respective study.

**Figure 3: The AUC of Indivdiual Significant OR Taxa to classify Carcinoma.** A) Fecal samples. B) Unmatched tissue samples. The larger circle represents the median AUC of all studies and the smaller circles represent the individual AUC for a particular study. The dotted line denotes an AUC of 0.5.

**Figure 4: Most Important Members in Significant OR Taxa Carcinoma Models.** A) Common taxa in the top 10 percent for carcinoma Random Forest fecal-based models. B) Common taxa in the top 10 percent for carcinoma Random Forest unmatched tissue-based models. Blue represents less important and red represents more important to the Random Forest Model. White means that particular taxa was not in the top 10%.

**Figure 5: Fecal Sample Random Forest Model Train AUCs.** A) Adenoma random forest model AUCs between all genera, all OTU, and select model based on significant OR taxa. B) Carcinoma random forest model AUCs between all genera, all OTU, and select model based on significant OR taxa. The black line represents the median AUC for the respective group. If no values are present in the singificant OR taxa group then there were no significant taxa identified and no model was tested.

**Figure 6: Fecal Sample Random Forest Genus-Based Model Test AUCs.** A) Test AUCs of adenoma models using all genera across study. B) Test AUCs of carcinoma models using all genera or significant OR taxa only. The black line represents the AUC at 0.5. The red lines represent the median AUC of all test AUCs for a specific study.

@@

**Figure S1: Odds Ratio for Adenoma or Carcinoma based on Bacterial Community Metrics in Tissue.** A) Community-based odds ratio for adenoma. B) Community-based odds ratio for carcinoma. Colors represent the different variable regions used within the respective study.

**Figure S2: Tissue Random Forest Model Train AUCs.** A) Adenoma random forest model AUCs between all genera, all OTU, and select model based on significant OR taxa in unmatched and matched tissue. B) Carcinoma random forest model AUCs between all genera, all OTU, and select model based on significant OR taxa in unmatched and matched tissue. The black line represents the median AUC for the respective group. If no values are present in the singificant OR taxa group then there were no significant taxa identified and no model was tested.

**Figure S3: Most Common Taxa Across Carcinoma Full Community Fecal Sample Study Models.** A) Common taxa in the top 10 percent for carcinoma Random Forest all taxa-based models. B) Common taxa in the top 10 percent for carcinoma Random Forest all OTU-based models. Blue represents less important and red represents more important to the Random Forest Model. White means that particular taxa was not in the top 10%.

**Figure S4: Most Common Genera Across Full Community Tissue Study Models.** A) Common genera in the top 10 percent for matched carcinoma Random Forest all genera-based models. B) Common genera in the top 10 percent for unmatched carcinoma Random Forest all genera-based models. C) Common genera in the top 10 percent for matched carcinoma Random Forest all OTU-based models. D) Common genera in the top 10 percent for unmatched carcinoma Random Forest all OTU-based models. Blue represents less important and red represents more important to the Random Forest Model. White means that particular taxa was not in the top 10%.

**Figure S5: Tissue Random Forest Genus-Based Model Test AUCs.** A) Test AUCs of adenoma models using all genera across study. B) Test AUCs of carcinoma models using all genera for matched tissue studies. C) Test AUCs of carcinoma models using all genera or significant OR taxa only for unmatched tissue studies The black line represents the AUC at 0.5. The red lines represent the median AUC of all test AUCs for a specific study.

>>>>

**Table 1: Characteristics of the datasets included in the fecal-based analysis**

@@

**Table 2: Characteristics of the datasets included in the tissue-based analyses**

@@

**Figure 1: Comparison of alpha diversity indices that were significant between individuals with normal colons, and those with adenomas or carcinomas using data collected from fecal samples** A) Comparison of evenness between individuals with normal colons and adenomas. B) Comparison of evenness between individuals with normal colons and carcinomas. C) Comparison of Shannon diversity between individuals with normal colons and carcinomas. Blue points represent individuals with normal colons and red points represent individuals with either adenomas (panel A) or carcinomas (panel B and C). The black lines represent the median value for each group.

**Figure 2: Comparison of odds ratios calculated using alpha diversity community metrics associated with the presence of adenomas (A) or carcinoma (B) relative to those in individuals with normal colons using data collected from stool samples.**

**Figure 3: AUC values when classifing individuals as having normal colons or carcinomas using taxa with significant ORs when using stool samples (A) and unmatched tissue samples (B).** We did not identify any taxa as having a significant OR to differentiate individuals with normal colons and adenomas or using matched tissue samples. The large black circles represent the median AUC of all studies and the smaller circles represent the individual AUC for a particular study. The dotted line denotes an AUC of 0.5.

**Figure 4: Comparison of Random Forest modeling approaches to classify individuals as having normal colons or adenomas (A) or carcinomas (B) when training the models using the taxa with significant ORs, all taxa in a community, or all OTUs in a community when using stool samples.** No taxa had a significant OR associated with the presence of adenomas using stool samples. The black line represents the median AUC for the respective group. The dashed gray line indicates an AUC of 0.5.

**Figure 5: Relative importance of taxa with significant ORs in Random Forest models for differentiating between individuals with normal colons and carcinomas using stool samples (A) or unmatched tissue samples (B).** The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure 6: Testing of Random Forest models to classify individuals as having normal colons or adenomas (A) or carcinomas (B) when using sequence data obtained from stool samples.** Models were trained on data from each study (Figure 5) and tested on the other studies. The black lines represent the median AUC of all test AUCs for a specific study. The dashed gray line represents the AUC at 0.5.

@@

**Figure S1:  Comparison of Odds Ratios associated with normal colons or adenomas (A) or carcinomas (B) calculated using alpha diversity indices with sequence data generated from tissue samples.** The pooled results are from the aggregation of data across all studies. The horizontal lines indicate the 95% confidence interval for the OR.

**Figure S2: Relative importance of taxa (A) and OTUs (B) in Random Forest models for differentiating between individuals with normal colons and carcinomas using stool samples.** These taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure S3: Relative importance of taxa (A, B) and OTUs (C, D) in Random Forest models for differentiating between individuals with normal colons and carcinomas using matched (A, C) and unmatched (B, D) tissue samples.** hese taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure S4: Comparison of Random Forest modeling approaches to classify individuals as having normal colons or adenomas (A) or carcinomas (B) when training the models using the taxa with significant ORs, all taxa in a community, or all OTUs in a community when using data from tissue samples.** No taxa had a significant OR associated with the presence of adenomas using tissue samples. The black line represents the median AUC for the respective group. The dashed gray line indicates an AUC of 0.5.

**Figure S5: Testing of Random Forest models to classify individuals as having normal colons or adenomas (A) or carcinomas (B, C) when using sequence data obtained from tissue samples.** Models were trained on data from each study (Figure S5) and tested on the other studies. The black lines represent the median AUC of all test AUCs for a specific study. The dashed gray line represents the AUC at 0.5.

### 2018-03-15 submission/supplemental.Rmd
update to include normal not control fig 1

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stooland Tissue**

@@

table_s1 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")), 
         comparison = "Adenoma", 
         sample_type = "Stool") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

colnames(table_s1) <- c("F statistic", "R2", "P-value", "Study", "Tumor", "Sample Type")

@@

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")), 
         comparison = "Carcinoma", 
         sample_type = "Stool") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

colnames(table_s2) <- c("F statistic", "R2", "P-value", "Study", "Tumor", "Sample Type")

@@

table_s3 <- temp_t3a %>% 
  bind_rows(temp_t3b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Lu", "Flemer", "Lu (Matched)"), 
         comparison = "Adenoma", 
         sample_type = "Tissue") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Tumor", "Sample Type")

@@

table_s4 <- temp_t4a %>% 
  bind_rows(temp_t4b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Sanapareddy", "Burns", "Flemer", "Chen", 
                   "Dejea (Matched)", "Geng (Matched)", "Burns (Matched)"), 
         comparison = "Carcinoma", 
         sample_type = "Tissue") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

colnames(table_s4) <- c("F statistic", "R2", "P-value", "Study", "Tumor", "Sample Type")

@@

**Table S2: Alpha Diversity Metrics OR in Tissue**

colnames(alpha_RR_adn_tissue) <- c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure", 
                                   "Tumor", "Tissue Group")

colnames(alpha_RR_crc_unmatch_tissue) <- c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure", 
                                           "Tumor", "Tissue Group")

colnames(alpha_RR_crc_match_tissue) <-  c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure", 
                                          "Tumor", "Tissue Group")

**Table S3: OR of Tumor in Stool by Individual Genera with Initial P-Value under 0.05**

@@

temp_8 <- read_csv("../data/process/tables/adn_select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Adenoma") %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure, comparison)

colnames(temp_8) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Taxa ID", "Tumor")

temp_10 <- read_csv("../data/process/tables/select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma") %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure, comparison)

colnames(temp_10) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Taxa ID", "Tumor")

@@

**Table S4: OR of Tumor in Tissue by Individual Genera with Initial P-Value under 0.05**

@@

temp_9 <- read_csv("../data/process/tables/adn_select_genus_OR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Adenoma", 
         tissue_type = "Combined") %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure, comparison, tissue_type)

colnames(temp_9) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Taxa ID", 
                      "Tumor", "Tissue Group")

temp_11 <- read_csv("../data/process/tables/select_genus_OR_unmatched_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma", 
         tissue_type = "Unmatched") %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure, comparison, tissue_type)

colnames(temp_11) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Taxa ID", 
                      "Tumor", "Tissue Group")

temp_12 <- read_csv("../data/process/tables/select_genus_OR_matched_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma", 
         tissue_type = "Matched") %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure, comparison, tissue_type)

colnames(temp_12) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Taxa ID", 
                      "Tumor", "Tissue Group")

@@

>>>>

**Table S1: Comparison of odds ratios calculated using alpha diversity community metrics associated with the presence of adenomas or carcinoma relative to those in individuals with normal colons using data collected from tissue samples.**

colnames(alpha_RR_adn_tissue) <- c("Odds Ratio", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "Measure", 
                                   "Tumor", "Tissue Group")

colnames(alpha_RR_crc_unmatch_tissue) <- c("Odds Ratio", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "Measure", 
                                           "Tumor", "Tissue Group")

colnames(alpha_RR_crc_match_tissue) <-  c("Odds Ratio", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "Measure", 
                                          "Tumor", "Tissue Group")

**Table S2: Comparison of community dissimilarity between individuals with normal colons and those with adenomas and carcinomas as calculated using Bray-Curtis distance and tested using PERMANOVA.**

@@

table_s1 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")), 
         comparison = "Adenoma", 
         sample_type = "Feces") %>% 
  select(study, comparison, sample_type, r2, pvalue)

colnames(table_s1) <- c("Study", "Tumor", "Sample Type", "R2", "P-value")

@@

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")), 
         comparison = "Carcinoma", 
         sample_type = "Feces") %>% 
  select(study, comparison, sample_type, r2, pvalue)

colnames(table_s2) <- c("Study", "Tumor", "Sample Type", "R2", "P-value")

@@

table_s3 <- temp_t3a %>% 
  bind_rows(temp_t3b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Lu", "Flemer", "Lu (Matched)"), 
         comparison = "Adenoma", 
         sample_type = "Tissue") %>% 
  select(study, comparison, sample_type, r2, pvalue)

colnames(table_s3) <- c("Study", "Tumor", "Sample Type", "R2", "P-value")

@@

table_s4 <- temp_t4a %>% 
  bind_rows(temp_t4b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Sanapareddy", "Burns", "Flemer", "Chen", 
                   "Dejea (Matched)", "Geng (Matched)", "Burns (Matched)"), 
         comparison = "Carcinoma", 
         sample_type = "Tissue") %>% 
  select(study, comparison, sample_type, r2, pvalue)

colnames(table_s4) <- c("Study", "Tumor", "Sample Type", "R2", "P-value")

@@

**Table S3: ORs for individual taxa associated with individuals who had a normal colon or adenomas or carcinomas using data collected from stool.** The listed P-values were less than 0.05 prior to using a Benjimani-Hochberg correction for multiple comparisons.

@@

temp_8 <- read_csv("../data/process/tables/adn_select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Adenoma") %>% 
  select(measure, comparison, rr, ci_lb, ci_ub, pvalue, bh)

colnames(temp_8) <- c("Taxon", "Tumor", "OR", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "BH")

temp_10 <- read_csv("../data/process/tables/select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma") %>% 
  select(measure, comparison, rr, ci_lb, ci_ub, pvalue, bh)

colnames(temp_10) <- c("Taxon", "Tumor", "OR", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "BH")

@@

\blandscape

**Table S4: ORs for individual taxa associated with individuals who had a normal colon or adenomas or carcinomas using data collected from tissue samples.** The listed P-values were less than 0.05 prior to using a Benjimani-Hochberg correction for multiple comparisons.

@@

temp_9 <- read_csv("../data/process/tables/adn_select_genus_OR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Adenoma", 
         tissue_type = "Combined") %>% 
  select(measure, comparison, tissue_type, rr, ci_lb, ci_ub, pvalue, bh)

colnames(temp_9) <- c("Taxon", "Tumor", "Tissue Group", "OR", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "BH")

temp_11 <- read_csv("../data/process/tables/select_genus_OR_unmatched_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma", 
         tissue_type = "Unmatched") %>% 
  select(measure, comparison, tissue_type, rr, ci_lb, ci_ub, pvalue, bh)

colnames(temp_11) <- c("Taxon", "Tumor", "Tissue Group", "OR", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "BH")

temp_12 <- read_csv("../data/process/tables/select_genus_OR_matched_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_unclassified", ""), 
         comparison = "Carcinoma", 
         tissue_type = "Matched") %>% 
  select(measure, comparison, tissue_type, rr, ci_lb, ci_ub, pvalue, bh)

colnames(temp_12) <- c("Taxon", "Tumor", "Tissue Group", "OR", "95% CI (Lower Bound)", "95% CI (Upper Bound)", "P-value", "BH")

@@

\elandscape
\newpage
